### 2015-12-15 introduction.tex
Fix grammar

Finally, in Section~\ref{subsection:mirror-descent-lower-bound}, we show
negative results for existing popular variants of \textsc{MD}. We show two
examples that demonstrate variants of \textsc{MD} can have $\Omega(T)$ regret
(on sequences of loss vector of unit norm) if the Bregman divergence associated
with the regularizer is unbounded.  First example demonstrates
$\Omega(T^{3/2})$ regret of the standard gradient descent with step size
$1/\sqrt{t}$, \textsc{AdaGrad MD} and \textsc{Scale-Free MD} on a unbounded
decision set.  Second example demonstrates $\Omega(T)$ regret for
\textsc{Scale-Free MD} for learning with expert advice with negative entropy
regularizer.  Both results indicate that \textsc{FTRL} is superior to
\textsc{MD}.

>>>>

Finally, in Section~\ref{subsection:mirror-descent-lower-bound}, we show
negative results for existing popular variants of \textsc{MD}. We show two
examples that demonstrate that variants of \textsc{MD} can have $\Omega(T)$
regret (on sequences of loss vectors of unit norm) if the Bregman divergence
associated with the regularizer is unbounded.  First example demonstrates
$\Omega(T^{3/2})$ regret of the standard gradient descent with step size
$1/\sqrt{t}$, \textsc{AdaGrad MD} and \textsc{Scale-Free MD} on a unbounded
decision set.  Second example demonstrates $\Omega(T)$ regret for
\textsc{Scale-Free MD} for learning with expert advice with negative entropy
regularizer.  Both results indicate that \textsc{FTRL} is superior to
\textsc{MD}.
